COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-11-27 main.tex
Update discussion of figures 4 and 5

Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved. Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs. During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}. To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference. By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates. The dashed lines again represent the libration width of each resonance and are meant to show its range of influence. In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR. Interestingly, the 3:1 MMR only appears to have a noticemable influence on the collision rate in the EJ simulation. (Better check if this is still true when I rerun CJ with smaller steps). In both cases, the 5:3 MMR appears to slightly enhance the collision rate interior to the nominal resonance location. It is important to keep in mind, however that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce nonphysical boundary effects.

Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that is produced will end up. To do so, we will operate under the assumption that dust grains produced by collision events will quickly couple to the gas and attain a circular orbit. This assumption, which will be further justified in section \ref{sec:dust}, allows to map the radial variation in the dust surface density to the radial position of the collisions. This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision. Most notably, many of the prominent features visible in figure \ref{fig:coll_hist_a} no longer appear. This is due to the fact that the orbits of colliding bodies have a wide range of eccentricities. In the CJ simulation, there are prominent dips in the collision rate centered around the 2:1 and 3:1 MMR. Although still visible in the EJ simulation, these dips are much wider and shallower. This is due to the fact that particles near the edge of the region of influence of the MMRs have a higher eccentricity in the secularly forced disk. Because a larger eccentricity allows collisions to happen over a broader range of radial distances, the sharp, well-defined edges of the trough centered around the resonances becomes washed out.

>>>>

Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved. Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs. During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}. To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference. By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates. The dashed lines again represent the libration width of each resonance and are meant to show its range of influence. In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR. The 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation. In both cases, although the 5:3 MMR has a clear influence on the on the semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate. It is important to point out, however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce boundary effects.

Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that is produced will end up. To do so, we will operate under the assumption that dust grains produced by collision events will quickly couple to the gas and attain a circular orbit. This assumption, which will be further justified in section \ref{sec:dust}, allows to map the radial variation in the dust surface density to the radial position of the collisions. This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.

Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear. This is due to the fact that the orbits of bodies in the 2:1 MMR have a wide range of eccentricities and therefore have the potential to undergo collisions at a wide range of heliocentric distances. In the CJ simulation, there is a prominent dip in the collision rate near the 2:1 MMR. This feature is still moderately visible in the EJ simulation, but the dip is much wider and shallower. The random orientations of the orbits inside of the resonance (see figure \ref{fig:long_ph}), combined with the forced eccentricites of planetesimals adjacent to the resonance weakens the dip near the 2:1 MMR seen in the left hand panel of figure \ref{fig:coll_hist_a}. Additionally, there is a double-pronged feature in the collision rate near the 3:1 MMR in the EJ simulation. The radial distance of these two prongs corresponds to the maximum radial excursion that a planetesimal at the 3:1 MMR with an eccentricity set by secular forcing with Jupiter undergoes. (Need more explanation of why this happens)
